### 2016-07-25 Chapters/introduction.tex
Remove useless pages, reorganize some parts

\textit{There's an infinity of things that have never been done before, and
most of those things are not worth doing.} -- Jeremy Fox

@@

The theory of evolution has deeply changed biology.\\
\textit{Very broad introduction on how we use evolution to actually make sense of biology}

We are still trying to understand the fundamental forces that shape life in all its diversity.\\
\textit{Evolution through natural selection is a verbal theory, and people have been trying to formalize it for 200 years.
It implies working and looking for "the hand of evolution" at several scales, from population to molecular biology.
It is challenging to translate the mechanisms of natural selection (fitness) at every scale, hence the problems to uncover fundamental properties of life.}
%Since its invention, huge efforts have been made to put Darwin's theory into equation, in order to clarify our understanding, to see how it apply at different scales (species, populations, cells, molecules...).

Microorganisms exhibits the most fundamental features of life. 
\textit{They are open systems that take energy from the environment around them, and use it to maintain and reproduce their structures.
They live literally everywhere. They represent a perfect model organism for fundamental questions.}

They also managed to become the thoughest of all the living systems.
\textit{Their diversity allow them to colonize every biotope, but remarkably, a single species can live in broad conditions, growing on different carbon sources or resist to really harmful environments.}

Their capacity to survive and exploit strong environmental fluctuations lay on another ubiquitous process of life as we know it: gene expression.
\textit{Short explanation on DNA, RNA, Protein and the regulations behind, that can be seen as loading "programs" depending on the environment the organism as to cope with.}

Such a mechanism can be seen as a resource allocation problem.
\textit{Limited protein production capacity, so choice have to be made for what need to be produced, natural selection selecting for the best strategies.}

>>>>

\textit{There's an infinity of things that have never been done before, and
most of those things are not worth doing.} -- Jeremy Fox, \textit{Dynamic Ecology}, 2016

@@

%The theory of evolution has deeply changed biology.\\
%\textit{Very broad introduction on how we use evolution to actually make sense of biology}
%
%We are still trying to understand the fundamental forces that shape life in all its diversity.\\
%\textit{Evolution through natural selection is a verbal theory, and people have been trying to formalize it for 200 years.
%It implies working and looking for "the hand of evolution" at several scales, from population to molecular biology.
%It is challenging to translate the mechanisms of natural selection (fitness) at every scale, hence the problems to uncover fundamental properties of life.}
%%Since its invention, huge efforts have been made to put Darwin's theory into equation, in order to clarify our understanding, to see how it apply at different scales (species, populations, cells, molecules...).

Microorganisms exhibits the most fundamental features of life. 
\textit{They are open systems that take energy from the environment around them, and use it to maintain and reproduce their structures.
They live literally everywhere, have the same metabolism, etc...
They represent a perfect model organism for fundamental questions.}

They also managed to become the thoughest of all the living systems.
\textit{Their diversity allow them to colonize every biotope, but remarkably, a single species can live in broad conditions, growing on different carbon sources or resist to really harmful environments (even space!).
}

Their capacity to survive and exploit strong environmental fluctuations lay on another ubiquitous process of life as we know it: self-catalysis and gene expression.
\textit{Short explanation on DNA, RNA, Protein and the regulations behind, that can be seen as loading "programs" depending on the environment the organism as to cope with.}

Such a mechanism can be seen as a resource allocation problem.
\textit{Because they can build everything from a single carbon source.
But they have a limited protein production capacity, so choice have to be made for what need to be produced, natural selection selecting for the best strategies.}

### 2016-07-25 Chapters/theory.tex
Remove useless pages, reorganize some parts

\section{Steady-state analysis of model}
\label{sec:methods_model_analysis}

@@

\section{Model fitting}
\label{sec:methods_model_fitting}

@@

\section{Solution of optimal control problem}

@@

\section{Specification and analysis of control strategies}

@@

\subsubsection{Model formulation}

@@

\subsubsection{Nondimensionalization of the system}

@@

\subsubsection{Steady-state growth of the self-replicator}
\label{si::growthrate}

@@

\subsubsection{Maximization of growth rate at steady state}
\label{si::optimal}

@@

\subsubsection{Analysis of the control strategies}
\label{si::control_strategies}

@@

\subsubsection{Precursor-only strategy}

@@

\subsubsection{On-off strategy}

@@

\subsubsection*{\Large \texorpdfstring{$e_M$}{eM}}

@@

\subsubsection*{\Large \texorpdfstring{$k_R$}{kR}}

@@

\subsubsection*{\Large \texorpdfstring{$K_R$}{KR}}

@@

\subsubsection*{\Large \texorpdfstring{$\beta$}{Beta}}

@@

\subsubsection*{\Large \texorpdfstring{$E_M$}{EM} and \texorpdfstring{$K$}{K}}

@@

\subsubsection{Statement of the problem}

@@

\subsubsection{Maximum Principle}
Necessary conditions on optimal trajectories can be obtained by the Infinite Horizon Maximum Principle~\cite{carlson_infinite_1991}.
Let $H(\hat{p},\hat{r},\lambda_p,\lambda_r,\lambda_0,\alpha)$ be the Hamiltonian of the system, defined by
\[
H(\cdot) \equiv \lambda_p\, E_M\, (1-\hat{r}) - \hat{r}\, \dfrac{\hat{p}}{K+\hat{p}}\left[\lambda_p (1+\hat{p}) +\lambda_r\, \hat{r} +\lambda_0\right] + \alpha \, \lambda_r \, \hat{r}\, \frac{\hat{p}}{K+\hat{p}}.
\]
Moreover, let $\alpha$ be an optimal control, and $\hat{x}(\cdot)=(\hat{p}(\cdot),\hat{r}(\cdot))$ the associated trajectory.
Then, there exists $\lambda_0 \leq 0$ and an absolutely continuous map $\lambda=(\lambda_p,\lambda_r):[0,+\infty) \rightarrow \mathbb{R}^2$
such that $(\lambda,\lambda_0)\neq0$, and
\begin{align}
\dot{\lambda}_p\, =-\frac{\partial H}{\partial \hat p}&= \hat{r} \, \frac{K}{(K+\hat{p})^2}\, \left[\lambda_p \, (1+\hat{p}) +\lambda_r\, ( \hat{r}-\alpha) + \lambda_0\right] + \hat{r}\, \frac{\hat{p}}{K+\hat{p}}\, \lambda_p, \label{eq:adjoint_p}\\
 \dot{\lambda}_r\, =-\frac{\partial H}{\partial \hat r}&= \lambda_p\, E_M +\frac{\hat{p}}{K+\hat{p}} \, \left[\lambda_p \, (1+\hat{p}) +\lambda_r\, (2 \hat{r}-\alpha) +\lambda_0\right] \label{eq:adjoint_r}.
\end{align}
The maximization condition is given by:
\begin{equation}{\label{eq:PMP}}
\begin{aligned}
&\alpha(\hat{t}) \in \arg\ max_{v \in [0,1]} H(\hat{x}(\hat{t}),\lambda(\hat{t}),\lambda_0,v), \\ &\mathrm{almost}\ \mathrm{everywhere}\ \mathrm{on}\ [0,+\infty).
\end{aligned}
\end{equation}

@@

\subsubsection{Characterization of singular arcs}

@@

\subsubsection{Analysis of the adjoint system}
Recalling that a switch corresponds to a change of sign of $\lambda_r$, the analysis of the adjoint system (Eqs~\ref{eq:adjoint_p}-\ref{eq:adjoint_r}) may be useful to characterize the switches of extremal trajectories.

@@

\subsubsection{Optimal trajectories}

>>>>

\subsection{Steady-state analysis of model}
\label{sec:methods_model_analysis}

@@

\subsection{Model fitting}
\label{sec:methods_model_fitting}

@@

\subsection{Solution of optimal control problem}

@@

\subsection{Specification and analysis of control strategies}

@@

\subsection{Model formulation}

@@

\subsection{Nondimensionalization of the system}

@@

\subsection{Steady-state growth of the self-replicator}
\label{si::growthrate}

@@

\subsection{Maximization of growth rate at steady state}
\label{si::optimal}

@@

\subsection{Analysis of the control strategies}
\label{si::control_strategies}

@@

\subsection{Precursor-only strategy}

@@

\subsection{On-off strategy}

@@

\subsection*{\Large \texorpdfstring{$e_M$}{eM}}

@@

\subsection*{\Large \texorpdfstring{$k_R$}{kR}}

@@

\subsection*{\Large \texorpdfstring{$K_R$}{KR}}

@@

\subsection*{\Large \texorpdfstring{$\beta$}{Beta}}

@@

\subsection*{\Large \texorpdfstring{$E_M$}{EM} and \texorpdfstring{$K$}{K}}

@@

\subsection{Statement of the problem}

@@

\subsection{Maximum Principle}
Necessary conditions on optimal trajectories can be obtained by the Infinite Horizon Maximum Principle~\cite{carlson_infinite_1991}.
Let $H(\hat{p},\hat{r},\lambda_p,\lambda_r,\lambda_0,\alpha)$ be the Hamiltonian of the system, defined by
\[
H(\cdot) \equiv \lambda_p\, E_M\, (1-\hat{r}) - \hat{r}\, \dfrac{\hat{p}}{K+\hat{p}}\left[\lambda_p (1+\hat{p}) +\lambda_r\, \hat{r} +\lambda_0\right] + \alpha \, \lambda_r \, \hat{r}\, \frac{\hat{p}}{K+\hat{p}}.
\]
Moreover, let $\alpha$ be an optimal control, and $\hat{x}(\cdot)=(\hat{p}(\cdot),\hat{r}(\cdot))$ the associated trajectory.
Then, there exists $\lambda_0 \leq 0$ and an absolutely continuous map $\lambda=(\lambda_p,\lambda_r):[0,+\infty) \rightarrow \mathbb{R}^2$
such that $(\lambda,\lambda_0)\neq0$, and
\begin{align}
\dot{\lambda}_p\, =-\frac{\partial H}{\partial \hat p}&= \hat{r} \, \frac{K}{(K+\hat{p})^2}\, \left[\lambda_p \, (1+\hat{p}) +\lambda_r\, ( \hat{r}-\alpha) + \lambda_0\right] + \hat{r}\, \frac{\hat{p}}{K+\hat{p}}\, \lambda_p, \label{eq:adjoint_p}\\
 \dot{\lambda}_r\, =-\frac{\partial H}{\partial \hat r}&= \lambda_p\, E_M +\frac{\hat{p}}{K+\hat{p}} \, \left[\lambda_p \, (1+\hat{p}) +\lambda_r\, (2 \hat{r}-\alpha) +\lambda_0\right] \label{eq:adjoint_r}.
\end{align}
The maximization condition is given by:
\begin{equation}{\label{eq:PMP}}
\begin{aligned}
&\alpha(\hat{t}) \in \arg\ max_{v \in [0,1]} H(\hat{x}(\hat{t}),\lambda(\hat{t}),\lambda_0,v), \\ &\mathrm{almost}\ \mathrm{everywhere}\ \mathrm{on}\ [0,+\infty).
\end{aligned}
\end{equation}

@@

\subsection{Characterization of singular arcs}

@@

\subsection{Analysis of the adjoint system}
Recalling that a switch corresponds to a change of sign of $\lambda_r$, the analysis of the adjoint system (Eqs~\ref{eq:adjoint_p}-\ref{eq:adjoint_r}) may be useful to characterize the switches of extremal trajectories.

@@

\subsection{Optimal trajectories}
